FinalManuscript_DISCS_UG

### 2019-04-29 parts/00_abstract.tex
Final revisions and cleanup

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

>>>>

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Eesults have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for logarithm intensity transformation.

### 2019-04-29 parts/01_introduction_01contextofstudy.tex
Final revisions and cleanup

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. Cryptosystems allow plaintexts, data which is commonly understood, to be encrypted as ciphertext, data which can only be understood by authorized parties using a key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel.

@@

 Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure. The result of the operations can be recovered when the data is decrypted.. In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with general digital data, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. Various cryptosystems have been developed, which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.

@@

 Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure. The result of the operations can be recovered when the data is decrypted. In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}. There is additional interest in being able to perform image manipulation operations on encrypted images such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. While secure linear image operations have been implemented \cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as certain methods of illumination processing \cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain. This study in particular focuses on facial recognition.

### 2019-04-29 parts/01_introduction_02researchquestions.tex
Final revisions and cleanup

By implementing homomorphic cryptosystems and creating an OpenCV library so they can be easily used, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?

More specifically, our research will address the following sub-questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations? 
\end{enumerate}

>>>>

By creating a sofware library which implements various homomorphic cryptosystems, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?

Specifically, the study addresses the following research sub-questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
\end{enumerate}

### 2019-04-29 parts/01_introduction_03objectives.tex
Final revisions and cleanup

Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

>>>>

Previous attempts in the literature to provide privacy-preserving image processing tasks have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data~\cite{ziad_cryptoimg:_2016,hutchison_privacy-preserving_2009}. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear image operations.

Our main research objective is the assessment of the practicality of various homomorphic cryptosystems with regard to image processing on faces. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we 
\begin{enumerate}
    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a software library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

### 2019-04-29 parts/01_introduction_04significanceofstudy.tex
Final revisions and cleanup

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.

>>>>

This study investigates one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.

### 2019-04-29 parts/01_introduction_05scopeandlimitations.tex
Final revisions and cleanup

\section{Scope and Limitations of the Study}
Our study will test a fixed set of cryptosystems and image processing operations. 
We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear intensity adjustment (logarithm, power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
To test for image quality, we will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

>>>>

\section{Scope and Limitations of the Study}
The study tests a fixed set of cryptosystems and image processing operations. 
We test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear intensity adjustment (logarithm, power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
To test for image quality, we adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-29 parts/02_relatedliterature.tex
Final revisions and cleanup

We will now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations. Then, we will describe our target applications in image processing and facial recognition.

@@

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which we can implement.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
\end{enumerate}

>>>>

We now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations. We then describe our target applications in image processing and facial recognition.

@@

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for division, multiplication, and exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which can be approximated.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
\end{enumerate}

### 2019-04-29 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Final revisions and cleanup

\section{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we investigate methods required to approximate the logarithm and power functions. Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

>>>>

\section{Image Intensity Transformations}
% We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel intensity value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which we investigate in Appendix \ref{chap:logarithm_approximation}. Non-linear intensity transformations have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

### 2019-04-29 parts/02_relatedliterature_03facialrecognition.tex
Final revisions and cleanup

Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations. A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.

Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.

>>>>

Since simple image operations an be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations. A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.

Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.

### 2019-04-29 parts/02_relatedliterature_04homomorphiccryptosystems.tex
Final revisions and cleanup

A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on three sets: the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$ A \textit{plaintext}, an element of the \textit{plaintext space}, is text that can be commonly understood within a larger group. Given a \textit{key}, an element of the \textit{key space}, the encryption function maps a plaintext to some \textit{ciphertext}, an element of the ciphertext space which can only be understood by authorized parties. The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key. By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.

@@

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function which uses a private key $l$. The cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \label{eq:homomorphic_definition_encryption}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we can see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    \label{eq:homomorphic_definition_decryption}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts. Using a homomorphic cryptosystem, secure computation can be achieved by encrypting plaintexts and then operating on the ciphertexts. We note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems can be classified according to the supported plaintext operation(s) $\boxplus$ which can be securely computed. The cryptosystem is said to be \textit{additively homomorphic} if the plaintext operation $\boxplus$ is addition, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Homomorphic cryptosystems which only allow for a limited set of operations to be computed securely are called \textit{partially homomorphic} while those which allow for arbitrary operations to be computed securely are called \textit{fully homomorphic}. Numerous partially homomorphic and fully homomorphic cryptosystems have been developed in the literature. This study will compare several of them, which we will now introduce in detail.

>>>>

A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on plaintexts, ciphertexts and keys. A \textit{plaintext} is text that can be commonly understood within a larger group. Given a \textit{key}, the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties. The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropriate key. By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropriate keys, secure data transmission can be achieved.

@@

Homomorphic cryptosystems are a special type of cryptosystem which allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts. This allows for secure computation in the plaintext space $\mathcal{P}$, the set of all plaintexts, by performing operations in the ciphertext space $\mathcal{C}$, the set of all ciphertexts.

Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ is the decryption function which uses a private key $l$. The cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \label{eq:homomorphic_definition_encryption}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    \label{eq:homomorphic_definition_decryption}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts. Using a homomorphic cryptosystem, secure computation can be achieved by encrypting plaintexts and then operating on the ciphertexts. We note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems can be classified according to the supported plaintext operation(s) $\boxplus$ which can be securely computed. The cryptosystem is said to be \textit{additively homomorphic} if the plaintext operation $\boxplus$ is addition, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Homomorphic cryptosystems which only allow for a limited set of operations to be computed securely are called \textit{partially homomorphic} while those which allow for arbitrary operations to be computed securely are called \textit{fully homomorphic}. Numerous partially homomorphic and fully homomorphic cryptosystems have been developed in the literature. This study compares several of them, which we will now introduce in detail.

### 2019-04-29 parts/02_relatedliterature_05partiallyhomomorphic.tex
Final revisions and cleanup

\subsection{Floating-Point Arithmetic using PHE}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation. In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the addition and multiplication of integers in a PHE scheme, respectively.

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
	\begin{align*}
		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
		&= \frac{1}{2}E\left(2xy\right)\\
		&= E\left(xy\right).
	\end{align*}
\end{itemize}

>>>>

\subsection{Floating-Point Arithmetic using PHE}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation. In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the secure addition and multiplication of integers in a PHE scheme, respectively.

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
	\begin{align*}
		E\left(\left(x+r\right)^2+ \left(-2rx + r^2\right)\right) = E\left(x^2\right).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E\left(\frac{1}{2}\left(\left(x+y\right)^2\ - x^2 - y^2\right)\right) 
		&= E\left(xy\right).
	\end{align*}
\end{itemize}

### 2019-04-29 parts/02_relatedliterature_06fullyhomomorphic.tex
Final revisions and cleanup

We will also be testing fully homomorphic encryption (FHEs), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that FHE are possible, although they are known to be significantly slower than PHE. 
Improving the efficiency of FHis an active area of research \cite{sen_homomorphic_2013}.

We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe important developments and implementations of each cryptosystem.

>>>>

We also test fully homomorphic encryption (FHE), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that FHE are possible, although they are known to be significantly slower than PHE.
Improving the efficiency of FHE is an active area of research \cite{sen_homomorphic_2013}.

We will present two FHE schemes, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe important developments and implementations of each cryptosystem.
